---
title: "Lab 8"
author: "Lucy Genua"
date: '2018-03-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load the packages
```{r}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)

```


###Column graph of Texas oil spills
```{r}
oil_spills<-read_csv("oil_spills.csv")

#COOL NOTE: When your column headers have spaces, you can call them with angled apostrophes (symbol under the squiggly, top left of keyboard)

df<-oil_spills %>% 
  filter(`Accident State` =="TX" & `Accident Year`<2017) %>% 
  group_by(`Accident Year`) %>% 
  summarise(Loss=sum(`Net Loss (Barrels)`))

colnames(df)<-c("Year", "Loss")

ggplot(df, aes(x=Year, y=Loss))+
  geom_col()
```

###Leaflet plot of spill locations in Texas in 2016
```{r}
df_loc<-oil_spills %>% 
  filter(`Accident State`=="TX" & `Accident Year`==2016) %>% 
  select(Latitude, Longitude, `Net Loss (Barrels)`)

colnames(df_loc)<-c("latitude", "longitude", "net_loss")


#CONVERT TO SPATIAL DATA FROM LAT/LONG 
oil_sf<-st_as_sf(df_loc, coords=c("longitude", "latitude"), crs=4326)

leaflet(oil_sf) %>% 
  addTiles() %>% 
  addMarkers()

```

###tmap plot with the Texas state shapefile
```{r}
states<-st_read(dsn=".", layer="states")

tex_border<-states %>% 
  filter(STATE_NAME=="Texas") %>% 
  st_transform(4326)
#Transform so that it has the same crs as the point data  

st_crs(tex_border)

plot(tex_border) #5 non-geometry attributes. 

tm_shape(tex_border)+
  tm_polygons()+
  tm_shape(oil_sf)+
  tm_dots(size=0.3)
```

###Convert the data to spatial points patterns (combination of point data and the bounding window) so that you can do quadrat test, nearest neighbours
```{r}
spill_spatial<-as(oil_sf, "Spatial") #Turn this back into spatial points data frame
spill_ppp<-as(spill_spatial, "ppp") #Turn into ppp (point pattern data)

tx_spatial<-as(tex_border, "Spatial")
tx_owin<-as(tx_spatial, "owin") #Turn into outer window

all_ppp<-ppp(spill_ppp$x, spill_ppp$y, window=tx_owin) #x and y are the columns with lat and long


```

###Make a density plot
```{r}
plot(density(all_ppp, sigma=0.4)) #sigma sets radius of bubbles. Can totally change someone's interpretation. Be careful. 
```

###Quadrat test for spatial evenness (see lecture slides for why this is not a good test of complete spatial randomness)
```{r}
oil_qt<-quadrat.test(all_ppp, nx=5, ny=5) #5 horizontal regions, 5 vertical
oil_qt
#Based on this test, we would reject null hyp of CSR/evenly distributed (this test is really testing for evenness, not CSR - see lecture)

plot(all_ppp)
plot(oil_qt, add=TRUE, cex=0.4) #Run these lines at the same time
#It's cool that it changes the expected proportion for partial quadrants.

```


###Nearest neighbour analysis with G-function (only considers one nearest neighbour)

Recall: If data are more clustered than CSR, nearest neighbours are closer together on average. If data are more uniform than CSR, nearest neighbours are farther apart on average. 

```{r}
#Allison has already determined an appropriate range for r distances. Would be different for other data. 
r<-seq(0,1, by=0.01)

oil_gfun<-envelope(all_ppp, fun=Gest, r=r, nsim=100) #nsim=100 runs 100 simulations with a Poisson distribution (the distribution of CSR data)

attributes(oil_gfun)

ggplot(oil_gfun, aes(x=r, y=obs))+
  geom_line(color="black")+
  geom_line(aes(x=r, y=theo), color="red")

#Observed data has higher proportion of point pairs with nearest neighbours at shorter distances to each other than CSR.

```

###Nearest neighbour using the L-function (A.K.A. Ripley's K, standardized)

```{r}
r2<-seq(0,3,by=0.5) #L function is more computationally intensive, so we chose large increment so the simulations won't take too long to run in lab

oil_lfun<-envelope(all_ppp, fun=Lest, r=r2, nsim=20) #Again, we chose low number of simulations for the sake of saving time in lab. On your own you'd want to do more.

ggplot(oil_lfun, aes(x=r2, y=obs))+
  geom_line(color="black")+
  geom_line(aes(x=r2, y=theo), color="blue") #Looks bad because our increments are too big. 
```


